---
title: "Reduce Sugar Consumption"
author: "Karin Altvater, Santosh Bhandari, Patrick Frey, Sanghyo Moon"
date: "2023-06-23"
output:
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Sugar Sweetened Beverages (SSBs)

-   soft drinks, energy drinks, fruit nectar drinks etc.
-   many associated health issues → decrease life quality of individual people → burden on the public health system

## SSB TAX

-   to internalize the external costs of high sugar consumption
-   higher prices of SSBs →
    -   lower consumption: proven for several countries
    -   tax returns can be reinvested in health sector

## Countries with SSB tax

```{r ,include=F, echo=F}
library(tmap)
data(World)
library(readxl)
library(raster)
library(sp)

SSB_Tax_Database_Feb23 <- read_excel("Sanghyo/SSB-Tax-Database-Feb23.xlsx")
SSB_World <- merge(World, SSB_Tax_Database_Feb23, by.x="iso_a3", by.y="wb_code")

A <- tm_shape(World)+
  tm_polygons()+
  tm_shape(SSB_World)+
  tm_polygons("SSB-Tax")+
  tm_layout(main.title = "Countries with SSB -Tax",
            main.title.position = "center",
            main.title.color = "#003333")+
  tm_text(text = "iso_a3", size = 0.2)

```

```{r }
A
```

As we can see, there is [no SSB tax in Germany.]{.underline}

## Decision

### **Decision**: Introduction of a tax on SSBs in germany

### **Decision maker**: German government

## Our Model

```{r ,include=F, echo=F}
library(decisionSupport)
library(DiagrammeR)

model_SSB <- grViz("digraph {
compound=true
graph[layout = dot, rankdir = LR]
node[style = filled, margin = 0.1, fillcolor = 'azure', shape = rectangle]
tax                     [label = 'Sugar tax for SSB']
tax -> cultivation_sugarbeet[lhead = cluster_assumptions]
less_consum_SSB         [label = 'less consumption of SSB']
less_consum_sug         [label = 'less consumption of Sugar']
less_prod_sug           [label = 'less production of Sugar']
 cultivation_sugarbeet   [label = 'decreased sugar beet cultivation']
 turnover_sugarbeet      [label = 'decreased turnover of sugar beets']
 decreased_SSB_products  [label = 'decreased of SSB products']
 decrease_SB_farmer      [label = 'decrease of sugar beet farmers']
 area                    [label = 'Increased areas for sustainable cultivations']
  soil                    [label = 'changed soil properties']
  obecity                 [label = 'decreased obecity']
  govtax                  [label = 'higher tax returns for the goverment']
  loss_SSB_prod           [label = 'loss for SSB producers']
  subgraph cluster_assumptions { 
  graph[rankdir = LR, label = 'Assumptions',
  fontsize = 28, shape = rectangle, style = dashed,
   fontcolor = grey]
   
   less_consum_SSB -> less_consum_sug
   subgraph cluster_economic {
    graph[rankdir = TD, label = 'Economic',
    fontsize = 28, shape = rectangle, style = dashed,
     fontcolor = grey, color = orange]
     
  cultivation_sugarbeet -> turnover_sugarbeet
  less_prod_sug -> cultivation_sugarbeet
  cultivation_sugarbeet -> decrease_SB_farmer
   govtax
   loss_SSB_prod
   decreased_health_cost
   }
   
  less_consum_SSB -> decreased_SSB_products
  subgraph cluster_ecologic { 
  graph[rankdir = TD, label = 'Ecologic',
  fontsize = 28, shape = rectangle, style = dashed,
  fontcolor = grey, color = green]
  turnover_sugarbeet -> area, soil
  }
  
  subgraph cluster_social { 
  graph[rankdir = TD, label = 'Social',
  fontsize = 28, shape = rectangle, style = dashed,
  fontcolor = grey, color = blue]
  demo          [label = 'Demonstration against the tax']
  gab           [label = 'Increases gab between poor and rich']
  }
  subgraph cluster_health { 
  graph[rankdir = TD, label = 'Health',
  fontsize = 28, shape = rectangle, style = dashed,
  fontcolor = grey, color = red]
  less_consum_sug -> obecity, less_prod_sug
  }
  }
NPV
}")
      

```


```{r, echo=F}
model_SSB
```

