---
title: "16.06. Presentation"
author: "Team. Nutrition"
date: "2023-06-15"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Countries with Sugar Sweetend Beverage Tax

```{r ,include=F, echo=F}
library(tmap)
data(World)
library(readxl)
SSB_Tax_Database_Feb23 <- read_excel("Sanghyo/SSB-Tax-Database-Feb23.xlsx")
SSB_World <- merge(World, SSB_Tax_Database_Feb23, by.x="iso_a3", by.y="wb_code")
A <- tm_shape(World)+
  tm_polygons()+
  tm_shape(SSB_World)+
  tm_polygons("carbonates")+
  tm_layout(main.title = "Countries with SSB -Tax",
            main.title.position = "center",
            main.title.color = "lightblue")+
  tm_text(text = "iso_a3", size = 0.2)

```

```{r }
A
```


## Input modell
```{r echo=F}
library(decisionSupport)
library(DiagrammeR)
grViz("digraph {
  
graph[layout = dot, rankdir = LR]
node[style = filled, margin = 0.1, fillcolor = 'azure']


I   [label = 'Input for Decision']
pos [label = 'Positiv Support', fillcolor = 'green']
neg [label = 'Negativ Support', fillcolor = 'red']

sh  [label = 'Stakeholder', shape = rectangle]
res [label = 'Results of Countries', shape = rectangle]

gov [label = 'Goverment', shape = rectangle]
ind [label = 'Individuals', shape = rectangle]
sm [label = 'Supermarkets', shape = rectangle]
man [label = 'Manufactories', shape = rectangle]

rs  [label = 'Research', shape = rectangle]

gov, ind, sm, man -> sh -> pos, neg
rs -> res
res -> pos, neg 
pos, neg -> I

}")
```

## Hey


